Global phase diagram and possible quantum spin liquid in the triangular $J-K-\Gamma$ model

### 2020-01-02 paper/paper.tex
20200102 14:49:10

\begin{figure}
    \includegraphics[width=0.45\textwidth]{Fig4.pdf}
    \caption{(Color online) Map of the probabilities.}
     \label{fig:Proabilities}
\end{figure}

>>>>

\begin{figure}
    \includegraphics[width=0.45\textwidth]{Fig4.pdf}
    \caption{(Color online) Map of the probabilities of the cluster spin-coherent state given by Eq.\eqref{eq:ClusterCoherentState} in varies exact cluster GS. The radial and polar coordinate gives the angles $\theta$ and $\phi$, which are spherical angles with respect to the reference frame shown in Fig. \ref{fig:ModelDefinition}(c). The green dashed lines and solid circles mark the ordered moment direction determined for the classical states, see main text for details. (a)-(b) Probability maps for the FM states in the \emph{FM-A} and \emph{FM-C} phase, respectively. (c)-{f} Proability maps for the stripe states in the \emph{Stripe-A}, \emph{Stripe-B}, \emph{Stripe-C}, \emph{Stripe-D}, resepctively.}
     \label{fig:Proabilities}
\end{figure}
